Supplemental data to ``ARTICLE TITLE''

### 2022-10-13 additional_files/additional_file_1.tex
Improve the contingency tables for haplotypes and phenotypes in k-mer plots; adjust the the genomic range of some k-mer plots
Add functionality for plotting the pairwise LD between k-mers; add such a plot for flower color
Specify the figures to be made in the Makefile dynamically from the ones listed in the additional file
Remove some figures from the additional data file; save the correspondence between haplotypes and phenotypes to file in figures/kmer_plot.R; extend the reference signal found by de Ronne et al.
Refine the results for the final analysis; add a script for the fine analysis of

\newcommand{\signalplot}[1]{
\begin{cfigure}
	\caption[Figure caption]{Figure caption}
	\includegraphics[width = 6in]{#1_signal}
	\label{#1_signal}
\end{cfigure}

@@

@@

% \caption[Number of SVs per Oxford Nanopore sample]{{{{

%\begin{table}
%	\caption[Number of SVs per Oxford Nanopore sample]{}
%	\label{table_s1}
%
%	\begin{threeparttable}\small
%			   \begin{tablenotes}
%			   \end{tablenotes}
%	\end{threeparttable}
%
%\end{table}
%\clearpage%}}}

% Manhattan plots of all traits
\manhattanplot{stem_termination_all}
\manhattanplot{stem_termination_sn}
\manhattanplot{pubescence_color_all}
\manhattanplot{pubescence_color_nogray}
\manhattanplot{protein}
\manhattanplot{pubescence_form_all}
\manhattanplot{pubescence_form_noerect}
\manhattanplot{oil}
\manhattanplot{pubescence_density}
\manhattanplot{seed_coat_luster_all}
\manhattanplot{seed_coat_luster_nointermediate}
\manhattanplot{seed_coat_luster_dullshiny}
\manhattanplot{pod_color_all}
\manhattanplot{pod_color_blbr}
\manhattanplot{flower_color}
\manhattanplot{seed_coat_color_all}
\manhattanplot{seed_coat_color_greenyellow}
\manhattanplot{hilum_color_all}
\manhattanplot{hilum_color_blackbrown}
\manhattanplot{hilum_color_rbr}
\manhattanplot{maturity_group}
\manhattanplot{corrected_dry_weight}

\signalplot{pca_t}
\signalplot{fc_w}
\signalplot{sda_dt1}

>>>>

% Defining a new command for signal plot figures
\newcommand{\signalplot}[1]{
\begin{cfigure}
	\includegraphics[width = 6in]{#1_signal}
	\caption{#1\_signal}
	\label{#1_signal}
\end{cfigure}

@@

% Defining a new command for gene plot figures
\newcommand{\geneplot}[1]{
\begin{cfigure}
	\includegraphics[width = 6in]{#1_gene}
	\caption{#1\_gene}
	\label{#1_gene}
\end{cfigure}

% Defining a new command for k-mer plot figures
\newcommand{\kmerplot}[1]{
	\begin{cfigure}
		\includegraphics[width = 6.5in]{#1_kmers}
		\caption{#1\_kmers}
		\label{#1_kmers}
	\end{cfigure}

% Defining a new command for LD plot figures
\newcommand{\ldplot}[1]{
	\begin{cfigure}
		\includegraphics[width = 6.5in]{#1_ld}
		\caption{#1\_ld}
		\label{#1_ld}
	\end{cfigure}

% Allows underscores in captions but is not a great solution
\catcode`_=12

@@

\begin{landscape} \footnotesize
	\begin{ThreePartTable}

		\begin{TableNotes}
		\item[a] test
		\end{TableNotes}

		\begin{longtable}{llcclccccl}

			\caption{Signals}\\
			\label{signals_table}\\

			\toprule
			Trait & Locus & Chromosome & -log10(p) & Gene & Platypus & vg & Paragraph & k-mers  & Study \\
			\midrule \endfirsthead

			\caption[]{Signals \emph{(continued)}}\\

			\toprule
			Trait & Locus & Chromosome & -log10(p) & Gene & Platypus & vg & Paragraph & k-mers  & Study \\
			\midrule
			\endhead

			\bottomrule
			Continued on next page \\
			\endfoot

			\bottomrule \insertTableNotes
			\endlastfoot
			\csvreader[head to column names,
			late after line=\\,
			late after last line=,
			before reading={\catcode`\#=12},
			after reading={\catcode`\#=6},
			/csv/separator=semicolon]%
			{../tables/signals_table.csv}{}{\Trait & \Locus & \Chromosome & \Pvalues & \Gene & \Platypus & \Vg & \Paragraph & \Kmers & \Study}

		\end{longtable}

	\end{ThreePartTable}

\end{landscape}
\clearpage

\gwastableone{FLOWER.COLOR}
\gwastabletwo{PUBESCENCE.COLOR}
\gwastabletwo{SEED.COAT.COLOR}
\gwastabletwo{STEM.TERMINATION.TYPE}
\gwastablethree{HILUM.COLOR}
\gwastabletwo{POD.COLOR}
\gwastabletwo{PUBESCENCE.FORM}
\gwastableone{PUBESCENCE.DENSITY}
\gwastablethree{SEED.COAT.LUSTER}
\gwastableone{MATURITY.GROUP}

% Figures for flower color
\manhattanplot{flower_color}
\ldplot{flower_color}
\signalplot{flower_color_W1}
\geneplot{flower_color_W1}
\kmerplot{flower_color_W1}

% Figures for pubescence color
\manhattanplot{pubescence_color_all}
\signalplot{pubescence_color_all_T}
\geneplot{pubescence_color_all_T}
\kmerplot{pubescence_color_all_T}
\ldplot{pubescence_color_all}

\manhattanplot{pubescence_color_nogray}
\signalplot{pubescence_color_nogray_Td}
\geneplot{pubescence_color_nogray_Td}
\kmerplot{pubescence_color_nogray_Td}

% Figures for seed coat color
\manhattanplot{seed_coat_color_all}
\signalplot{seed_coat_color_all_I}

\manhattanplot{seed_coat_color_greenyellow}
\signalplot{seed_coat_color_greenyellow_G}
\geneplot{seed_coat_color_greenyellow_G}
\kmerplot{seed_coat_color_greenyellow_G}

% Figures for stem termination
\manhattanplot{stem_termination_all}
\signalplot{stem_termination_all_Dt1}
\geneplot{stem_termination_all_Dt1}
\kmerplot{stem_termination_all_Dt1}

\manhattanplot{stem_termination_sn}
\ldplot{stem_termination_sn}
\signalplot{stem_termination_sn_stGm11}
\signalplot{stem_termination_sn_stGm16}
\signalplot{stem_termination_sn_stGm18}

% Figures for hilum color
\manhattanplot{hilum_color_all}
\signalplot{hilum_color_all_T}
\geneplot{hilum_color_all_T}
\kmerplot{hilum_color_all_T}
\signalplot{hilum_color_all_I}
\geneplot{hilum_color_all_I}

\manhattanplot{hilum_color_blackbrown}
\signalplot{hilum_color_blackbrown_R}
\geneplot{hilum_color_blackbrown_R}
\kmerplot{hilum_color_blackbrown_R}

\manhattanplot{hilum_color_rbr}

% Figures for pod color
\manhattanplot{pod_color_all}
\signalplot{pod_color_all_L1}
\signalplot{pod_color_all_L2}

\manhattanplot{pod_color_blbr}
\ldplot{pod_color_blbr}
\signalplot{pod_color_blbr_pdcGm15}

% Figures for pubescence form
\manhattanplot{pubescence_form_all}
\signalplot{pubescence_form_all_Pa1}
\geneplot{pubescence_form_all_Pa1}
\kmerplot{pubescence_form_all_Pa1}
\signalplot{pubescence_form_all_Pa2}
\ldplot{pubescence_form_all}

\manhattanplot{pubescence_form_noerect}

% Figures for pubescence density
\manhattanplot{pubescence_density}
\signalplot{pubescence_density_Ps}
\geneplot{pubescence_density_Ps}

% Figures for seed coat luster
\manhattanplot{seed_coat_luster_all}

\manhattanplot{seed_coat_luster_nointermediate}

\manhattanplot{seed_coat_luster_dullshiny}
\ldplot{seed_coat_luster_dullshiny}
\signalplot{seed_coat_luster_dullshiny_B}
\geneplot{seed_coat_luster_dullshiny_B}

% Figures for corrected dry weight
\manhattanplot{corrected_dry_weight}
\ldplot{corrected_dry_weight}
\signalplot{corrected_dry_weight_cdwGm15}

% Figures for maturity group
\manhattanplot{maturity_group}

% Figures for oil
\manhattanplot{oil}

% Figures for protein
\manhattanplot{protein}
